---
title: "Nationally Determined Contributions (NDC) Text Analysis"
format: html
execute: 
  echo: true
  warning: false
  eval: true
embed-resources: true
---
.
This exercise aims to analyze the data from the reports on Nationally Determined Contributions (NDC) of seven Caribbean countries. The reports are in pdf files, which are read by the tessaeract package and processed for analysis. The text is tokenized and analyzed for n-grams, word frequency, and other relevant information. 

Loading the required libraries.

```{r}
# Libraries
library(dplyr)
library(magick)
library(pdftools)
library(reactable)
library(stringr) 
library(tesseract)
library(tidyr) 
library(tidytext) 
library(widyr)
library(wordcloud2)

```

Create a dictionary to map country abbreviations to full country names.

```{r}
dict_country <- data.frame(
    country_abbr = c("antigua", "barbados", "dominica", "grenada", "lucia", "vincent", "kitts"),
    country_name = c("Antigua and Barbuda", "Barbados", "Dominica", "Grenada", "Saint Lucia", "Saint Vincent and the Grenadines", "St. Kitts and Nevis"))
```


Read the pdf files for all countries and create a dataframe with the text.

You don't need to run this code block. The data is already saved as an RDS file and can be loaded in the next code block.

```{r}
#| eval: false
# Function to read text from PDF using Tesseract
read_pdf_tesseract <- function(pdf_path) {
  # Load the PDF
  pdf_info <- pdf_info(pdf_path)
  num_pages <- pdf_info$pages

  all_text <- ""
  
  for (page in 1:num_pages) {
    # Convert PDF page to image
    pdf_image <- pdf_render_page(pdf_path, page = page, dpi = 300)
    img <- image_read(pdf_image)
    
    # Perform OCR on the image
    text <- ocr(img)
    all_text <- paste(all_text, text, sep = "\n")
  }
  
  return(all_text)
}

# Specify the path to your PDF file
pdf_file_antigua <- "docs/ATG - UNFCCC NDC - 2021-09-02 - Final.pdf"
pdf_file_barbados <- "docs/2021 Barbados NDC update - 21 July 2021.pdf"
pdf_file_dominica <- "docs/The Commonwealth of Dominica updated NDC July 4 ,.pdf"
pdf_file_grenada <- "docs/GrenadaSecondNDC2020 - 01-12-20.pdf"
pdf_file_saint_lucia <- "docs/Saint Lucia First NDC (Updated submission).pdf"
pdf_file_saint_vincent <- "docs/Saint Vincent and the Grenadines_NDC.pdf"
pdf_file_st_kitts <- "docs/St. Kitts and Nevis Revised NDC_Updated.pdf"

pdf_files <- c(pdf_file_antigua, pdf_file_barbados, pdf_file_dominica, pdf_file_grenada, pdf_file_saint_lucia, pdf_file_saint_vincent, pdf_file_st_kitts)

# Read text from the PDF
pdf_texts <- list()

for (pdf_file in pdf_files) {
  pdf_text <- read_pdf_tesseract(pdf_file)

  pdf_texts[[pdf_file]] <- pdf_text
  print(pdf_file)
}

pdf_texts |> names()
pdf_texts2 <- pdf_texts

names(pdf_texts2) <- dict_country$country_abbr

pdf_texts2 |> names()


dim(pdf_texts2[[1]])
typeof(pdf_texts2[[1]])

df2 <- data.frame()

for (i in 1:length(pdf_texts2)) {

    df <- data.frame(country = names(pdf_texts2)[[i]], 
                     text = pdf_texts2[[i]]) 
    
    df2 <- df2 |> bind_rows(df)
}

dim(df2)

#saveRDS(df2, "data/ndc_pdf_text.rds")

```

Read the previously processed and saved RDS dataframe and then create tidy dataframes for n-grams and sentences for analysis.

```{r}
df2 <- readRDS("data/ndc_pdf_text.rds") 

df_tidy_n1 <- 
  df2 |>
  unnest_tokens(word, text) |> 
  mutate(ngram = 1)

df_tidy_n2 <- 
  df2 |>
  unnest_tokens(word, text, token = "ngrams", n = 2) |> 
  mutate(ngram = 2)

df_tidy_n3 <- 
  df2 |>
  unnest_tokens(word, text, token = "ngrams", n = 3) |> 
  mutate(ngram = 3)

df_tidy <- 
    df_tidy_n1 |>
    bind_rows(df_tidy_n2, df_tidy_n3) |> 
    left_join(dict_country, by = c("country" = "country_abbr"))

df_sentence <- 
    df2 |> 
    unnest_tokens(sentence, text, token = "sentences") 
```

Have a look at the sentence dataframe.

```{r}
df_sentence |> head(1000) |> reactable()
```

Exclude stop words and other words that are not relevant for the analysis.

```{r}
data("stop_words") # from tidytext 

stop_words_selected <- 
  c("1", "2", "3", "4", "15",
    "antigua", "barbuda", "7", "barbados", "the commonwealth",
    "5", "6", "ae", "ee",
    "vincent", "grenadines", "st", "saint",
    "kitts", "dominica", "nevis", "lucia",
    "grenada", "lucia’s", "to the", "of the", 
    "and the", "in the", "the commonwealth of", "for the",
    "nationally determined",
    "nationally determined contribution",
    "nationally determined contributions",
    "ndc",
    "ndcs",
    "nationally",
    "national",
    "grenada's",
    "grenada’s",
    "determined"
)

df_tidy2 <- 
    df_tidy |> 
    anti_join(stop_words) |> 
    filter(!word %in% stop_words_selected) |> 
    filter(!str_detect(word, "kitts|greanada|barbados|nevis|vincent|lucia|grenadines|dominica|saint|antigua|barbuda")) 

df_tidy_wc <- 
    df_tidy_n1 |> 
    anti_join(stop_words) |> 
    filter(!word %in% stop_words_selected) |> 
    filter(!str_detect(word, "kitts|greanada|barbados|nevis|vincent|lucia|grenadines|dominica|saint|antigua|barbuda")) 

```

# Wordclouds

For each country, create a wordcloud of the most frequent words in the dataframe.

```{r}
#| eval: false
library(wordcloud2)


wordclouds2 <- list()
for (i in 1:7) {
  word_data <- df_tidy2 |>
    filter(country == dict_country$country_abbr[i]) |>
    count(word) |>
    slice_max(n, n = 30)
    
  wc <- wordcloud2(
    word_data, 
    size = 0.5, 
    backgroundColor = "white", 
    color = "random-dark",
    widget_id = paste0("wordcloud_", i)  # Only works in dev version
  )
  
  wordclouds2[[i]] <- tagList(
    h2(dict_country$country_name[i]),
    div(style = "height: 400px;", wc)
  )
}

browsable(tagList(wordclouds2))



```


```{r}

library(ggwordcloud)
library(ggplot2)

# We'll store each plot in a list
plot_list <- list()

for (i in seq_len(nrow(dict_country))) {
  # Summarize data
  word_data <- df_tidy_wc |>
    filter(country == dict_country$country_abbr[i]) |>
    count(word, name = "freq") |>               # rename 'n' -> 'freq'
    slice_max(freq, n = 30)

  # Build the ggwordcloud
  p <- ggplot(word_data, aes(label = word, size = freq, color = freq)) +
    geom_text_wordcloud() +
    scale_size_area(max_size = 15) +
    theme_minimal() +
    ggtitle(dict_country$country_name[i])       # optional title

  # Store in our list
  plot_list[[i]] <- p
}

# Print all plots, one below the other
for (i in seq_along(plot_list)) {
  print(plot_list[[i]])
}


```

Focus on specific words and create a table with the frequency of these words for each country.

```{r}
search_elements <- c(
    "energy sector",
    "energy",
    "lulucf sector",
    "lulucf",
    "land use",
    "forestry",
    "forest", 
    "forests",
    "wetlands",
    "watershed",
    "agriculture sector",
    "agriculture",
    "gender",
    "adaptation", 
    "waste sector",
    "waste",
    "ippu",
    "industrial processes",
    "industrial processes and product use",
    "product use",
    "just transition",
    "transition",
    "urban",
    "health",
    "loss and damage",
    "children",
    "young people",
    "young",
    "youth",
    "circular economy",
    "circular",
    "green economy",
    "blue economy",
    "finance",
    "climate action",
    "voluntary cooperation",
    "voluntary",
    "mitigation", 
    "transparency", 
    "oceans", 
    "biodiversity", 
    "climate change")

df_search2 <- data.frame()

for (i in 1:length(search_elements)) {

df_search <- 
    df_tidy2 |> 
    filter(word == search_elements[i]) |>
    group_by(country_name) |>
    count() |> 
    mutate(search_element = search_elements[i])

df_search2 <- df_search2 |> bind_rows(df_search)

}

df_search2 |> pivot_wider(names_from = search_element, values_from = n) |> reactable()

```



```{r}
df_tidy2 |> filter(str_detect(word, "voluntary")) 

df_tidy2 |> 
    filter(str_detect(word, "mitigation")) |> 
    filter(ngram > 1) |>
    reactable()

df_sentence |> 
    filter(str_detect(sentence, "adaptation")) |>
    reactable()

df_sentence |> 
  filter(country == "lucia") |> 
  filter(str_detect(sentence, "voluntary")) |>
  reactable()

```

```{r}
reactable_list <- list()
country_list <- dict_country$country_abbr

for (i in 1:7) {

reactable_list[[i]] <-
  df_sentence |> 
  filter(country == country_list[[i]]) |> 
  filter(str_detect(sentence, "voluntary")) |>
  reactable()

}

```